Generate data for NOBA cod ensemble modeling

### 2020-03-25 NOBAcod.Rmd
atlantis code to get weight units

>>>>

This output is described in Atlantis code, file atlantis/atphysics/atagetracerIO.c, function `writeBMAnnAgeBioData`:

```
if (propit == out_nums_id) {  // Numbers case
                                for (b = 0; b < bm->nbox; b++) {
                                    val[b] = 0.0;
                                    for (k = 0; k < bm->wcnz; k++) {  // Sum over all individuals in the box
                                        val[b] += bm->wctr[b][k][id] * FunctGroupArray[sp].boxPopRatio[b][k][cohort][ai];
                                    }
                                }
                            } else  { // Size data - get weighted average of values per layer if numbers > min_dens
                                for (b = 0; b < bm->nbox; b++) {
                                    val[b] = 0.0;
                                    tot = 0.0;
                                    for (k = 0; k < bm->wcnz; k++) {  // Sum over all individuals in the box
                                        if (bm->wctr[b][k][id] > bm->min_dens) {
                                            val[b] += bm->wctr[b][k][id] * (bm->wctr[b][k][sn] + bm->wctr[b][k][rn]) * 5.7 * mg_2_g * FunctGroupArray[sp].boxPopRatio[b][k][cohort][ai];
                                            tot += bm->wctr[b][k][id];
                                        }
                                    }
                                    if (tot > 0.0)
                                        val[b] /= tot;
                                }
                            }
```

So weight output appears to be average weight at age in grams?
